---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(ggplot2)
```


## Overview

`"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc, and to visualize the probability distribution.

* `bin_variable()` prints the content of a binomial object
* `bin_probability`, `bin_distribution` and `bin_cumulative` calculates probability distribution of given binomial variable.
* `bin_mean`, `bin_variance`, `bin_mode`, `bin_skewness` and `bin_kurtosis` calculates summary measures for a given binomial object.
* `summary()` method for a binomail variable.
* `plot()` method for a binomial probability distribution.


## Motivation

This package has been developed to illustrate basic calculations of a Binomial variable.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("PeijieLi/binomial")
# install "binomial" (with vignettes)
devtools::install_github("PeijieLi/binomia", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)

# compute the probability of a binomail distribution
bin_probability(success = 2, trials = 5, prob = 0.5)

# compute the probability distribution of a binomial distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

# compute the cumulative probability distribution of a binomial distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

# construct a binomial object with given parameters
bin1 <- bin_variable(trials = 5, prob = 0.45)
binsum1 <- summary(bin1)
binsum1
```
