---
title: "Getting Started with Binomial"
author: "Peijie Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

## Binomial Distribution

The package `"binomial"` is a minimal implementation for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc, and to visualize the probability distribution.


## Creating a `Binomial` variable

The first step is to create a `"coin"` object with the function `coin()`:

```{r}
myBinomial <- bin_variable(trials = 5, prob = 0.5)
myBinomial
```

The function will print nicely the content of a `"binomial"` object.

The `summary()` function gives you detailed content about the `"binomial"` object:
```{r}
myBinomial <- bin_variable(trials = 10, prob = 0.3)
myBinomialSum <- summary(myBinomial)
myBinomialSum
```


## Calculating the Probability Distribution

You can calculate and visualize the probability distribution with the following functions:

```{r}
bin_distribution(trials = 5, prob = 0.4)
```

```{r}
bin_cumulative(trials = 5, prob = 0.4)
```

## Visualizing the Probability Distribution

You can use the function `plot()` to create a graohic for the calculated probability distribution:

```{r, fig.show='hold'}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```


```{r, fig.show='hold'}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```
